Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-05-01 PaperVictor.tex
Add \hl's removed by VIctor

Finally, Table \ref{tab:table3} shows data from some porous
silicon based ODM and quasi-ODM designed to operate in the NIR
region and their (quasi) ODB's are compared with those of
the structures analyzed in the present study. The quasi-ODW
of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
the quasi-ODB of the structure $S_3$ begins at 950 nm like the one
synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
nm. In other words, $S_3$ has a quasi-ODW 3.55 times larger. Moreover, the
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
\% of the quasi-ODW of our $S_2$ and $S_3$ structures. Aditionally, the table
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
As compared to the previous studies
\cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
opens the possibility of generating dielectric multilayered
structures with large quasi-omnidirectional bands with pairs of
materials that have a relatively low refractive index contrast. To be
fair, we have to point out that the (quasi-) omnidirectional band widths of the
structures compared above correspond to different angular ranges,
which are defined by instrumental constrictions.

\begin{table}
        \centering
        \begin{tabular}{rrrrrr}
                Reference&Year&Sample&\emph{q}-ODB (nm)&AR (degrees)&\emph{q}-ODW (nm)\\
                \hline
                \hline
                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&0-80&340\\
                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&0-89&318\\
                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&8-68&506\\
                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&8-65&1000\\
                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&0-80&1321\\
                \hline
                &    &$S_1$&980-1340&10-60&360 \\
                This work&2021&$S_2$&980-2780&10-60&1800\\
                &    &$S_3$&950-2750&10-60&1800\\
        \end{tabular}
        \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
                previously published works (first block) and for the different samples studied here (second
                block). We show the attained (quasi-) omnidirectional
                bands (\emph{q}-ODB), the measured angular range (AR) and their widths (\emph{q}-ODW).}
        \label{tab:table3}
\end{table}

@@

We have designed, optimized, fabricated and characterized highly reflective quasi-omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
spectral range. Two techniques, chirping (a continuous change in thicknesses) and
stacking of Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were
carried out employing the transfer matrix method and we optimized the
design parameters to obtain maximal reflectance averaged over different spectral ranges for
all angles.
We fabricated some of the optimized structures with
porous silicon
dielectric multilayers with low refractive contrast and compared their measured  optical properties
with the calculations. Two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
at 1160 nm and 1925 nm respectively have been shown. In addition,
we fabricated a stacked sub-Bragg mirror structure  with a quasi-omnidirectional bandwidth of 1800 nm (centered at 1850 nm) and a
thickness of 41.5 $\mu$m, which is almost two third (in thickness)
of the chirped structure.
Thus, our techniques allowed us to obtain relatively thin quasi-omnidirectional mirrors with wide bands
over different wavelength ranges.
Our analysis techniques can
be used for the optimization of the reflectance not only in multilayered PS systems with
different refractive index contrasts but also for systems with other types of
materials with low refractive index contrast. The present study could
also be useful for obtaining omnidirectional dielectric mirrors in
large spectral regions using different materials,  flat focusing
reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with
a wide angular independent response.

>>>>

Finally, Table \ref{tab:table3} shows data from some porous
silicon based ODM \hl{and quasi-ODM designed to operate in the NIR
region and their (quasi) ODB's are compared with those of
the structures analyzed in the present study. The quasi-ODW}
of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
\hl{the quasi-ODB of the structure $S_3$} begins at 950 nm like the one
synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
nm. In other words, $S_3$ has a quasi-ODW 3.55 times larger. Moreover, the
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
\% of the \hl{quasi-ODW of our $S_2$ and $S_3$ structures}. Aditionally, the table
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
As compared to the previous studies
\cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
opens the possibility of generating dielectric multilayered
\hl{structures with large quasi-omnidirectional bands with pairs of
materials that have a relatively low refractive index contrast. To be
fair, we have to point out that the (quasi-) omnidirectional band widths of the
structures compared above correspond to different angular ranges,
which are defined by instrumental constrictions.}

\begin{table}
        \centering
        \begin{tabular}{rrrrrr}
                Reference&Year&Sample&\emph{q}-ODB (nm)&\hl{AR (degrees)}&\emph{q}-ODW (nm)\\
                \hline
                \hline
                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&\hl{0-80}&340\\
                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&\hl{0-89}&318\\
                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&\hl{8-68}&506\\
                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&\hl{8-65}&1000\\
                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&\hl{0-80}&1321\\
                \hline
                &    &$S_1$&980-1340&\hl{10-60}&360 \\
                This work&2021&$S_2$&980-2780&\hl{10-60}&1800\\
                &    &$S_3$&950-2750&\hl{10-60}&1800\\
        \end{tabular}
        \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
                previously published works (first block) and for the different samples studied here (second
                block). We show the attained (quasi-) omnidirectional
                bands (\emph{q}-ODB), the measured angular range (AR) and their widths (\emph{q}-ODW).}
        \label{tab:table3}
\end{table}

@@

We have designed, optimized, fabricated and characterized highly
reflective quasi-omnidirectional (angular range of $0-60^\circ$)
multilayered structures with a wide
spectral range. Two techniques, chirping (a continuous change in thicknesses) and
stacking of Bragg-type sub-structures, have been used to enhance the
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were
carried out employing the transfer matrix method and we optimized the
design parameters to obtain maximal reflectance averaged over different spectral ranges for
all angles.
We fabricated some of the optimized structures with
porous silicon
dielectric multilayers with low refractive contrast and compared their measured  optical properties
with the calculations. Two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
at 1160 nm and 1925 nm respectively have been shown. In addition,
we fabricated a stacked sub-Bragg mirror structure  with a
quasi-omnidirectional bandwidth of 1800 nm centered at 1850 nm and a
thickness of 41.5 $\mu$m, which is almost two thirds as thick as the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands
over different wavelength ranges.
Our analysis techniques can
be used for the optimization of the reflectance not only in multilayered PS systems with
different refractive index contrasts but also for systems with other types of
materials with low refractive index contrast. The present study could
also be useful for obtaining omnidirectional dielectric mirrors in
large spectral regions using different materials,  flat focusing
reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with
a wide angular independent response.
